Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy

### 2017-03-07 paper/letter.tex
some typos

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

In this paper we show how the \tol's \lya\ profile can be explained
either by  or the recently developed class of complex multiphase models 
\citep{Gronke2016} or by a simple rotation model
\citep{GaravitoCamargo2014}. 
The models we use correspond to simplified geometrical configurations
to allow a deep exploration of parameter space and gain, for the firs time,
some physical insight into the \tol's kinematic properties.

@@

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range
(based on the considerations of \citep{Laursen2013ApJ...766..124L})
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented in
\citep{Gronke2016}.

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Maria Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

In this paper we show how the \tol's \lya\ profile can be explained
either by  or the recently developed class of complex multiphase models 
\citep{Gronke2016} or by a simple rotation model
\citep{GaravitoCamargo2014}. 
The models we use correspond to simplified geometrical configurations
to allow a deep exploration of parameter space and gain, for the first time,
some physical insight into the \tol's kinematic properties.

@@

In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range
(based on the considerations of \cite{Laursen2013ApJ...766..124L})
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented in
\citep{Gronke2016}.
